A thermodynamic view of dusty protoplanetary disks

### 2017-07-01 paper.tex
tweaked intro to fit restructure

This paper is organized as follows. 
%AY: or not? %We first present, without
%derivation, the correspondence between dusty gas and     
%ideal hydrodynamics in \S\ref{key_idea}. 
In \S\ref{grow_osc} 
we describe a key insight of our study, that pressure (i.e. ``PdV") work explains the basis of several instabilities, including SI and VSI, in terms of
pressure-density phase lags.   
%This means that dusty-gas phenomena, such 
%as SI and VSI, have thermodynamical interpretations.  
We begin our formal discussion in \S\ref{setup} by transforming the
basic equations describing tightly-coupled dusty gas into  hydrodynamic equations with a special cooling function. 
We derive equilibrium solutions in \S\ref{eqm}, which we use in our explicit stability calculations. In \S\ref{limits} we analyze the 
general stability properties of dusty disks. We then move onto
explicit stability analyses. In  
\S\ref{linear_problem} we show that our linearized equations 
reproduce the SGI and SI in the tight coupling regime. In \S\ref{results} we
extend the VSI to dusty disks. We   
discuss future applications of the dusty/adiabatic gas equivalence in 
\S\ref{discussion} before summarizing in \S\ref{summary}.

>>>>

This paper is organized as follows. 
%AY: or not? %We first present, without
%derivation, the correspondence between dusty gas and     
%ideal hydrodynamics in \S\ref{key_idea}. 
In \S\ref{grow_osc} 
we describe a key insight of our study, that pressure (i.e. ``PdV") work explains the basis of several instabilities, including SI and VSI, in terms of
pressure-density phase lags.   
%This means that dusty-gas phenomena, such 
%as SI and VSI, have thermodynamical interpretations.  
We begin our formal discussion in \S\ref{setup} by transforming the
basic equations describing tightly-coupled dusty gas into
hydrodynamic equations with a special cooling function.  Here we also
formalize the concept of dust-induced entropy and buoyancy. 
%We derive equilibrium solutions in \S\ref{eqm}, which we use in our
%explicit stability calculations.
In \S\ref{limits} we analyze the general stability properties of dusty
disks. We then move onto explicit stability analyses in
\S\ref{linear_problem}, were we show that dusty edges are unstable,
and revisit the SGI and SI in the tight
coupling regime. In \S\ref{results} we
extend the VSI to dusty disks. We   
discuss future applications of the dusty/adiabatic gas equivalence in 
\S\ref{discussion} before summarizing in \S\ref{summary}.
